The problem and promise of scale in multilayer networks

### 2020-01-22 paper/manuscript.Rmd
tweak methods

### Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer networks based on temporal (seasonal), spatial (habitat type), and social (visual and auditory perception). Caribou are gregarious ungulates with fission-fusion dynamics (Lesmerises et al. 2018) that display temporal (Peignier et al. 2019) and spatial (Webber et al. unpublished data) variation in social networks. In winter, caribou dig holes in the snow, termed craters to access forage (Bergerud 1974). As a result, caribou tend to occupy and re-use craters once they are established and there is considerably less access to forage than when the landscape is snow-free. Importantly, craters exist on the landscape at multiple scales: the crater scale (a single crater), the feeding area scale (multiple craters in close proximity), and the winter range scale (all craters within an individual’s range) (Mayor et al. 2009). The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou.

### Caribou location data
We used GPS location data collected from Fogo Island caribou in winter 2018 (1 January – 16 March). Adult female caribou were immobilized and fitted with global positioning system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars, 1,250 g) as described by Schaefer and Mahoney (2013). Collars were programmed to collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas et al. (2010). We did not collar all female caribou in the herd. However, we assumed that our sample of collared animals was random. Although associations between collared and uncollared animals were unrecorded, we assumed that our networks (see below) were unbiased representations of the relative degree of social association among all caribou.

@@

### Social network analysis
We used R package spatsoc (Robitaille et al. 2019) in *R version* (R CITATION) to generate proximity-based social networks (PBSN) from GPS telemetry data. We generated social networks for each herd in each season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al. 2018). We represented individuals in our networks by nodes and associations between individuals were represented by edges.

@@

### Variables/sensitivity

Unless otherwise mentioned, the spatial threshold is 50 and the temporal threshold is 5 minutes.

>>>>

### Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer networks based on temporal (seasonal), spatial (habitat type), and social (visual and auditory perception). Caribou are gregarious ungulates with fission-fusion dynamics (Lesmerises et al. 2018) that display temporal (Peignier et al. 2019) and spatial (Webber et al. unpublished data) variation in social networks. In winter, caribou dig holes in the snow, termed craters to access forage (Bergerud 1974). As a result, caribou tend to occupy and re-use craters once they are established and there is considerably less access to forage than when the landscape is snow-free. Importantly, craters exist on the landscape at multiple scales: the crater scale (a single crater), the feeding area scale (multiple craters in close proximity), and the winter range scale (all craters within an individual’s range) (Mayor et al. 2009). The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou. We therefore partitioned data into two discrete seasons: summer (DATES) and winter (DATES) based on caribou socioecology (Peignier et al. 2019).

### Caribou location data
We used GPS location data collected from Fogo Island caribou in winter 2018 (1 January – 16 March). Adult female caribou were immobilized and fitted with global positioning system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars, 1,250 g) as described by Schaefer and Mahoney (2013). Collars were programmed to collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas et al. (2010). We did not collar all female caribou in the herd; however, we assumed that our sample of collared animals was random.

@@

### Generating multilayer social networks
We used R package spatsoc (Robitaille et al. 2019) in *R version* (R CITATION) to generate proximity-based social network layers from GPS telemetry data (see above). We generated monolayer association networks for caribou in each habitat and season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al. 2018). We represented individuals in our networks by nodes and associations between individuals were represented by edges.

@@

Our multilayer social network therefore consisted of social association networks generated in two habitat types (open and closed) and in two seasons (winter and summer)

#### Generating multilayer social networks
